{Good covers and algebras on conically smooth spaces}

### 2025-09-10 paperversion/paper.tex
def of S_X and first properties

\newcommand{\R}{\mbb{R}}
\DeclareMathOperator{\Imm}{Im}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\dfnt}{\bfseries \itshape}
\newcommand{\hyph}{{\mbox{-}}}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Tangent}{\mathrm{T}}
\newcommand{\Normal}{\mathrm{N}}
\newcommand{\evv}{\mathrm{ev}}  
\DeclareMathOperator{\Unzip}{Unzip}
\DeclareMathOperator{\Link}{Link}
\DeclareMathOperator{\Span}{span}

@@

\begin{definition}
    $S_X\subset X$.
\end{definition}

>>>>

\newcommand{\R}{\mbb{R}}
\DeclareMathOperator{\Imm}{Im}
\newcommand{\id}{\mathrm{id}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\dfnt}{\bfseries \itshape}
\newcommand{\hyph}{{\mbox{-}}}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Tangent}{\mathrm{T}}
\newcommand{\Normal}{\mathrm{N}}
\newcommand{\evv}{\mathrm{ev}}  
\DeclareMathOperator{\Unzip}{Unzip}
\DeclareMathOperator{\Link}{Link}
\DeclareMathOperator{\Span}{span}
\newcommand{\opp}{{\mathrm{op}}}

@@

\begin{definition}
    Let $X$ be a CSS. Its \emph{singular locus} $S_X=\bigcup_{k>0} X_k\subset X$ consists of all points in $X$ which have strictly positive depth.
\end{definition}

\begin{lemma}
    For every CSS $X$, the inclusion $S_X\hookrightarrow X$ is a proper constructible embedding of conically smooth spaces.
\end{lemma}
\begin{proof}
    Let $X\to P$ be the stratification of $X$ and let $X\to P\to\mbb{P}=\mbb{Z}^{\opp}\times\mbb{Z}^{\opp}$ be its depth-dimension stratification \cite[Lemma 2.4.10]{ayala2017local}. The inclusion $\mbb{Z}_{>0}^{\opp}\subset\mbb{Z}^\opp$ (where in the subscript $>$ refers to the ordinary ordering and not to its opposite) is a full subcategory inclusion and is thus consecutive \cite[Definition 2.3.1]{ayala2017local}, hence so is $\mbb{P}_{+}=\mbb{Z}_{>0}^\opp\times\mbb{Z}^\opp\hookrightarrow\mbb{P}$. Since consecutive poset maps are stable under pullbacks, $\mbb{P}_{+}\times_{\mbb{P}}P\hookrightarrow P$ is likewise consecutive, proving that the inclusion $S_X=X|_{\mbb{P}_+\times_{\mbb{P}}P}\hookrightarrow X$ is a constructible map of conically smooth spaces \cite[Lemma 3.4.5, Example 3.4.7]{ayala2017local}. Finally, as $\mbb{Z}_{>0}^{\opp}\subset\mbb{Z}^\opp$ is downward-closed, $S_X$ is closed in $X$, so (since CSSs are Hausdorff) the inclusion map is proper.
\end{proof}
